Using Monte Carlo Algorithms to Achieve Resiliency \& Performance at Scale for Linear and Nonlinear Solver Applications

### 2016-01-26 doc/ecp/pres.tex
Changing CLF to CLT.
stuart: updating ecb slides

  \item Much of our analysis work has used and idealized
    advection-diffusion-reaction system that has properties common to these
    application areas

@@

\begin{frame}{Scaling - DD}

@@

\begin{frame}{Scaling - Replication}

@@

@@

  We have implemented a version of MCSA that uses GPUs to perform the MC
  linear solve.

  Distributed parallelism is enabled through an additive Schwartz method, all
  MC solves
  \begin{itemize}
  \item All MC random walks are local
  \item No inter-domain communication of histories
  \end{itemize}

@@

  \item Resiliency
    \begin{itemize}
    \item Replicated subsets enable useful work to occur at the same time as
      providing redundancy
    \item Yields protection against hard errors
    \end{itemize}
  \end{itemize}

@@

  Investigate use in time-dependent applications, e.g. non-linear radiation
  hydrodynamics for high-energy density physics applications:
  \begin{itemize}
  \item Used as inner linear solver in a non-linear (Newton) iteration
  \item Time-dependent applications generally have strong diagonal-dominance
    that makes MCSA competitive with Krylov methods
  \item MCSA has resiliency and parallel efficiency benefits over subspace
    methods
  \end{itemize}

@@

  \underline{\bf Trilinos}
  \begin{itemize}
  \item Provides abstract solver interface for MCLS
  \item Provides build system for Alea and MCLS
  \item Provides data structures and utilities for Alea and MCLS
  \end{itemize}

>>>>

  \item Much of our analysis work has used an idealized
    advection-diffusion-reaction system that has properties common to these
    application areas

@@

\begin{frame}{Scaling - Domain Decomposition}

@@

\begin{frame}{Scaling - Domain Replication}

  \vspace{-0.3in}

@@

  \vfill
  \begin{itemize}
  \item A single subset consisted of a domain decomposed problem on 256 cores
  \item Each additional subset replicates the original domain decomposed
    subset creating a heirarchy of replication and decomposition
  \end{itemize}

@@

  We have implemented a version of MCSA that uses GPUs to perform the MC
  linear solve.
  \vfill
  Distributed parallelism is enabled through an additive Schwartz method, all
  MC solves
  \begin{itemize}
  \item All MC random walks are local
  \item No inter-domain communication of histories
  \end{itemize}

@@

  \item Resiliency
    \begin{itemize}
    \item Replicated subsets enable useful work to occur at the same time as
      providing redundancy
    \item Yields algorithmic protection against hard errors
    \end{itemize}
  \end{itemize}

@@

  Investigate use in time-dependent applications, e.g. non-linear radiation
  hydrodynamics for high-energy density physics applications:
  \begin{itemize}
  \item Used as inner linear solver in a non-linear (Newton) iteration
  \item Time-dependent applications generally have strong diagonal-dominance
    that makes MCSA competitive with Krylov methods
  \item MCSA has resiliency and parallel efficiency benefits over conventional
    subspace methods
  \end{itemize}

@@

  \underline{\bf Trilinos}
  \begin{itemize}
  \item Provides abstract solver interface for MCLS
  \item Provides build system for Alea and MCLS
  \item Provides data structures and utilities for Alea and MCLS
  \item Provides testing harness for MCLS
  \end{itemize}
